\documentclass[10pt,a4paper]{article}
\input{packages}
\input{configuration}
\input{macros}

\title{Stratification of triangulated categories}
\author{Pieter Belmans}

\begin{document}
\maketitle

\tableofcontents

\section{Day 2: Infinite methods}
\subsection{Compact objects}
Let~$\mathcal{T}$ be a triangulated category, denote~$\Sigma$ its shift or suspension, and assume that~$\mathcal{T}$ has set-indexed coproducts.
\begin{definition}
  An object~$X$ of~$\mathcal{T}$ is \emph{compact} if~$\Hom_{\mathcal{T}}(X,-)\colon\mathcal{T}\to\Ab$ preserves coproducts.
\end{definition}
\begin{lemma}
  An object~$X$ is compact if and only if for all~$X\to\coprod_{i\in I}Y_i$ there exists a factorisation through~$\coprod_{i\in I}Y_i$, where~$I_0\subseteq I_0$ is a finite subset.
\end{lemma}
\begin{remark}
  These compact objects serve as building blocks for the category~$\mathcal{T}$ and they constitute a thick subcategory~$\mathcal{T}^\cc$.
\end{remark}
\begin{definition}
  The category~$\mathcal{T}$ is \emph{compactly generated} if~$\mathcal{T}=\Loc(\mathcal{C})$, for some set of compact objects~$\mathcal{C}$.
\end{definition}
\begin{proposition}
  For a set of compact objects~$\mathcal{C}\subseteq\mathcal{T}^\cc$ the following are equivalent:
  \begin{enumerate}
    \item $\Loc(\mathcal{C})=\mathcal{T}$;
    \item for all objects~$X$ in~$\mathcal{T}$ such that~$\Hom_{\mathcal{T}}(\Sigma^nC,X)=0$ for all objects~$C\in\mathcal{C}$ and~$n\in\mathbb{Z}$ we have~$X=0$.
  \end{enumerate}

  \begin{proof}
    From (1) to (2) is easy: let~$X$ be an object of~$\mathcal{T}$ and consider
    \begin{equation}
      % TODO improve notation
      {}^\perp X\coloneqq\left\{ V\in\mathcal{T}\mid\Hom_{\mathcal{T}}(\Sigma^nV,X)=0,\forall n\in\mathbb{Z} \right\}
    \end{equation}
    which is a localising subcategory of~$\mathcal{T}$. If~$\mathcal{C}\subseteq^\perp X$ then~$X=0$.

    From (2) to (1) we have to use Brown representability (see later), which depends on the compactness of the objects. The inclusion~$\Loc(\mathcal{C})\hookrightarrow\mathcal{T}$ has a right adjoint~$\Gamma$. Let~$X$ be an object of~$\mathcal{T}$, by the adjunction we have a morphism~$\Gamma(X)\to X$ that we can complete to a triangle
    \begin{equation}
      \Gamma(X)\to X\to X'\to
    \end{equation}
    and the long exact sequence obtained by applying~$\Hom_{\mathcal{T}}(V,-)$ tells us that~$\Hom_{\mathcal{T}}(V,X')=0$ for all~$X\in\Loc(\mathcal{C})$. So if (2) holds then we have~$X'=0$ and therefore~$X\in\Loc(\mathcal{C})$.% TODO improve the proof
  \end{proof}
\end{proposition}
\begin{proposition}
  Let~$X$ and~$Y$ be compact objects of~$\mathcal{T}$. If~$Y\in\Loc(X)$ then~$Y\in\Thick(X)$.
\end{proposition}
Hence if a compact objects~$Y$ can be obtained from a compact objects~$X$ in infinitely many steps it can also be done in finitely many.
\begin{example}
  Let~$A$ be any ring and take~$X\in\derived(\Mod/A)$. Then the following are equivalent:
  \begin{enumerate}
    \item $X\in\Thick(A)$;
    \item $X$ is isomorphic to a perfect complex;
    \item $X$ is compact.
  \end{enumerate}
\end{example}

\subsection{Brown representability}
\begin{theorem}
  Let~$\mathcal{T}$ be a compactly generated triangulated category. For a functor~$H\colon\mathcal{T}^\opp\to\Ab$ the following are equivalent:
  \begin{enumerate}
    \item $H$ is cohomological (i.e.\ it sends exact triangles to exact sequences and it sends coproducts to products);
    \item $H$ is representable (i.e.\ there exists an object~$X\in\mathcal{T}$ such that~$H\cong\Hom_{\mathcal{T}}(-,X)$).
  \end{enumerate}
\end{theorem}
\begin{corollary}
  Let~$\mathcal{T}$ be a compactly generated triangulated category. Then~$\mathcal{T}$ has all coproducts.
  \begin{proof}
    Consider~$\{X_i\}_{i\in I}$ a family of objects in~$\mathcal{T}$. Then~$\prod_{i\in I}\Hom_{\mathcal{T}}(-,X_i)$ satisfies condition (1) in the Brown representability theorem, hence it must be representable by an object that satisfies the universal property for a product.
  \end{proof}
\end{corollary}
\begin{corollary}
  Let~$\mathcal{T}$ be a compactly generated triangulated category and~$\mathcal{U}$ be any triangulated category. Then for all exact functors~$F\colon\mathcal{T}\to\mathcal{U}$ the following are equivalent:
  \begin{enumerate}
    \item $F$ preserves coproducts;
    \item $F$ admits a right adjoint~$G$.
  \end{enumerate}
  \begin{proof}
    From (1) to (2) we consider any object~$X$ in~$\mathcal{U}$, then~$\Hom_{\mathcal{U}}(F(-),X)\colon\mathcal{T}^\opp\to\Ab$ satisfies condition (1) in the Brown representability theorem, hence it can be represented as~$\Hom_{\mathcal{T}}(-,Y)$, and set~$G(X)\coloneqq Y$.

    From (2) to (1) is trivial as left adjoints preserve coproducts.
  \end{proof}
\end{corollary}
We will often take~$\mathcal{U}$ a Verdier quotient in applications.

\subsection{Bousfield localisation}
Let~$\mathcal{T}$ be a triangulated category and~$\mathcal{S}$ a thick subcategory. Its \emph{Verdier quotient}
\begin{equation}
  \mathcal{T}/\mathcal{S}\coloneqq\mathcal{T}[\{\sigma\in\Mor(\mathcal{T})\mid\cone(\sigma)\in\mathcal{S}\}^{-1}]
\end{equation}
is again triangulated, the quotient functor~$Q\colon\mathcal{T}\to\mathcal{S}$ is exact and its kernel~$\ker(Q)=\mathcal{S}$, where the \emph{kernel} and \emph{essential image}
\begin{equation}
  \begin{aligned}
    \ker(F)&\coloneqq\{X\in\mathcal{T}\mid F(X)=0\} \\
    \image(F)&\coloneqq\{Y\in\mathcal{U}\mid \exists X\in\mathcal{T}\colon Y\cong F(X)\}
  \end{aligned}
\end{equation}
are full triangulated subcategories.
\begin{example}
  Let~$\mathcal{A}$ be an abelian category. Then~$\derived(\mathcal{A})\coloneqq\mathbf{K}(\mathcal{A})/\mathbf{K}_\ac(\mathcal{A})$ is a triangulated category.
\end{example}
\begin{remark}
  A priori it is unclear whether a Verdier quotient~$\mathcal{T}/\mathcal{S}$ is locally small.
\end{remark}
\begin{definition}
   there is a natural transformation~$\eta\colon\identity_{\mathcal{T}}\Rightarrow L$ such that
  \begin{enumerate}
    \item $L\circ\eta\colon L\Rightarrow L^2$ is invertible, i.e.\ for all~$X$ the morphism~$L(\eta_X)\colon L(X)\to L^2(X)$ is an isomorphism;
    \item $L\circ\eta=\eta\circ L$, i.e.\ $L(\eta_X)=\eta_{L(X)}$.
  \end{enumerate}
\end{definition}
\begin{definition}
  A \emph{localisation functor} is an exact endofunctor~$\Gamma\colon\mathcal{T}\to\mathcal{T}$ for which~$\Gamma^\opp$ is a localisation functor.
\end{definition}
\begin{remark}
  The notation~$\Gamma$ is a reference both to Grothendieck's local cohomology functor and the symmetry between~$L$ and~$\Gamma$.
\end{remark}
\begin{proposition}
  For a thick subcategory~$\mathcal{S}$ the following are equivalent:
  \begin{enumerate}
    \item $\mathcal{S}\hookrightarrow\mathcal{T}$ admits a right adjoint;
    \item $Q\colon\mathcal{T}\to\mathcal{T}/\mathcal{S}$ admits a right adjoint;% TODO check these
    \item there exists a localisation functor~$L$ such that~$\ker(L)=\mathcal{S}$;
    \item there exists a colocalisation functor~$\Gamma$ such that~$\image(\Gamma)=\mathcal{S}$.
  \end{enumerate}
\end{proposition}
In this case, the following holds:
\begin{enumerate}
  \item for all objects~$X$ in~$\mathcal{T}$ there exists a functorial triangle
    \begin{equation}
      \Gamma(X)\to X\to L(X)\to
    \end{equation}
  \item $\mathcal{S}^\perp=\image(L)=\ker(\Gamma)$ and~${}^\perp(\mathcal{S}^\perp)=\mathcal{S}$ (where a priori the left-hand side could be bigger);
  \item $\Gamma$ induces a right adjoint for the inclusion~$\mathcal{S}\hookrightarrow\mathcal{T}$;
  \item $L$ induces a left adjoint for the inclusion~$\mathcal{S}^\perp\hookrightarrow\mathcal{T}$;
\end{enumerate}
\begin{remark}
  This is related to the notion of semi-orthogonal decompositions: we obtain~$\mathcal{T}=\langle\mathcal{S}^\perp,\mathcal{S}\rangle=\langle\mathcal{S},^\perp\mathcal{S}\rangle$. A useful mnemonic (suggested by Sasha Kuznetsov) is that~$\perp$ is always in the middle.
\end{remark}
\begin{example}
  Let~$\mathcal{T}$ be a compactly generated triangulated category. Let~$\mathcal{S}=\Loc(\mathcal{C})$ be a localising subcategory generated by a set of compact objects~$\mathcal{C}$. We obtain a diagram% TODO fix double headed
  \begin{equation}
    \begin{tikzcd}
      \mathcal{S}^\cc \arrow[hook]{r} \arrow[hook]{d} & \mathcal{T}^\cc \arrow{r} \arrow[hook]{d} & \mathcal{T}^\cc/\mathcal{S}^\cc \arrow{d} \\
      \mathcal{S} \arrow[hook]{r} & \mathcal{T} \arrow{r} & \mathcal{T}/\mathcal{S}
    \end{tikzcd}
  \end{equation}
  where~$\mathcal{S}^\cc=\Thick(\mathcal{C})$ and the induced functor~$\mathcal{T}^\cc/\mathcal{S}^\cc\to(\mathcal{T}/\mathcal{S})^\cc$ is an equivalence up to direct summands.
\end{example}

\subsection{Describing localising subcategories}
The problem that we would like to solve is the description of all localising subcategories of a compactly generated triangulated category. Some obvious questions that arise are:
\begin{enumerate}
  \item do they form a set or a proper class?
  \item how can we explicitly describe them?
\end{enumerate}

% TODO finish this last part


\section{Day 3: Stratification of big triangulated categories}
\subsection{Rings acting on triangulated categories}
Recall that for a commutative noetherian ring~$A$ we have the associated (big) derived category~$\derived(A)\coloneqq\derived(\Mod/A)$, and to an object~$X$ in~$\derived(A)$ we have associated a support~$\supp X$ and~$\cosupp X$ which are subsets of~$\Spec A$. This way we parametrise localising subcategories\fixthis{is this a summary or an announcement?}.
\begin{lemma}
  Let~$X$ and~$Y$ be objects of~$\derived(A)$. Then~$\supp X\subseteq \supp Y$ if and only if~$\Loc(X)\subseteq\Loc(Y)$.
\end{lemma}

\begin{lemma}
  Let~$X$ and~$Y$ be objects of~$\derived(A)$. Then~$\cosupp X\subseteq \cosupp Y$ if and only if~$\Coloc(X)\subseteq\Coloc(Y)$.\checkthis{I didn't copy the right hand side}
\end{lemma}

\begin{corollary}
  Let~$X$ and~$Y$ be objects of~$\derived(A)$. Then~$\Ext^\bullet(X,Y)=0$\checkthis{notation introduced?} if and only if~$\supp X\cap\cosupp Y=\emptyset$.
\end{corollary}

Now more generally, let~$\mathcal{T}$ be a triangulated category.
\paragraph{Problem} How can we determine that for~$X$ and~$Y$ objects in~$\mathcal{T}$ we have
\begin{equation}
  \Hom_{\mathcal{T}}^\bullet(X,Y)\coloneqq\bigoplus_{n\in\mathbb{Z}}\Hom_{\mathcal{T}}(X,\Sigma^nY)=0?
\end{equation}

Fix a~$\mathbb{Z}$\dash graded commutative ring~$R=\bigoplus_{n\in\mathbb{Z}}R^n$, i.e.\ we have~$rs=(-1)^{|r||s|}sr$ for~$r$ and~$s$ homogeneous elements. This graded-commutativity enters the picture because will often take~$R$ to be a cohomology ring.
\begin{definition}
  Let~$\mathcal{T}$ be a triangulated category and~$R$ a graded commutative ring. We say that~$\mathcal{T}$ is~\emph{$R$\dash linear}, or that~\emph{$R$ acts on~$\mathcal{T}$} if there is a homomorphism of rings
  \begin{equation}
    \varphi\colon R\to\centre^\bullet(\mathcal{T})
  \end{equation}
  where~$\centre^\bullet(\mathcal{T})$ is the \emph{graded centre} of~$\mathcal{T}$, which is the graded commutative ring whose degree~$n$ piece is given by
  \begin{equation}
    \centre^n(\mathcal{T})\coloneqq\left\{ \eta\colon\identity_{\mathcal{T}}\Rightarrow\Sigma^n\mid\eta\circ\Sigma=(-1)^n\Sigma\circ\eta \right\}.
  \end{equation}
\end{definition}
So for an object~$X$ of~$\mathcal{T}$ we get a ring homomorphism
\begin{equation}
  \varphi_X\colon R\to\End_{\mathcal{T}}^\bullet(X)
\end{equation}
and~$\Hom_{\mathcal{T}}^\bullet(X,Y)$ is a graded~$R$\dash module via~$\varphi_X$ acting on the right and~$\varphi_Y$ acting on the left, whose actions coincide up to a sign.

\paragraph{Standing assumptions} From now on we take~$R$ a graded commutative noetherian ring, $\mathcal{T}$ a compactly generated triangulated category and~$\Spec R$ the set of graded prime ideals of~$R$ (which might be confusing at first for algebraic geometers).

To a graded ideal~$\mathfrak{a}$ we assign
\begin{equation}
  \VV(\mathfrak{a})\coloneqq\left\{ \mathfrak{p}\in\Spec R\mid\mathfrak{a}\subseteq\mathfrak{p} \right\}
\end{equation}
and an~$R$\dash module~$M$ is \emph{$\mathfrak{a}$\dash torsion} if~$M_{\mathfrak{p}}=0$ for all~$\mathfrak{p}\in\Spec R\setminus\VV(\mathfrak{a})$, which is equivalent to the usual definition of torsion.

A subset~$V$ is \emph{specialisation-closed} if for all~$\mathfrak{p}\subseteq\mathfrak{q}$ such that~$\mathfrak{p}\in V$ we have~$\mathfrak{q}\in V$.

\begin{definition}
  An object~$X$ of~$\mathcal{T}$ is \emph{$V$\dash torsion} if~$\Hom_{\mathcal{T}}^\bullet(C,X)_{\mathfrak{p}}=0$ for all~$\mathfrak{p}\in\Spec R\setminus V$ and all~$C\in\mathcal{T}^\cc$.

  We then set
  \begin{equation}
    \mathcal{T}_V\coloneqq\left\{ X\in\mathcal{T}\mid\text{$X$ is $V$\dash torsion} \right\}
  \end{equation}
  which is a localising subcategory as the vanishing condition uses compact objects.
\end{definition}

\begin{proposition}
  For a specialisation-closed subset~$V$ there are
  \begin{enumerate}
    \item a localisation functor~$\LL_V\colon\mathcal{T}\to\mathcal{T}$ such that~$\ker\LL_V=\mathcal{T}_V$,
    \item a colocalisation functor~$\Gamma_V\colon\mathcal{T}\to\mathcal{T}$ such that~$\image\Gamma_V=\mathcal{T}_V$,
  \end{enumerate}
  such that we obtain a \emph{localisation triangle}
  \begin{equation}
    \Gamma_V(X)\to X\to\LL_V(X)\to
  \end{equation}
  for all objects~$X$ in~$\mathcal{T}$.
\end{proposition}

For~$\mathfrak{p}\in\Spec R$ we set the \emph{localisation} of an object~$X$ of~$\mathcal{T}$ at~$\mathfrak{p}$ to be
\begin{equation}
  X_{\mathfrak{p}}\coloneqq\LL_{\ZZ(\mathfrak{p})}(X)
\end{equation}
where~$\ZZ(\mathfrak{p})\coloneqq\{\mathfrak{q}\mid\mathfrak{q}\nsubseteq\mathfrak{p}\}=\Spec R\setminus\Spec R_{\mathfrak{p}}$. The natural map~$X\to X_{\mathfrak{p}}$ obtained from the adjunction induces an isomorphism
\begin{equation}
  \Hom_{\mathcal{T}}^\bullet(C,X)_{\mathfrak{p}}\cong\Hom_{\mathcal{T}}^\bullet(C,X_{\mathfrak{p}})
\end{equation}
for all compact objects~$C$ in~$\mathcal{T}$.

\begin{definition}
  We say that an object~$X$ of~$\mathcal{T}$ is \emph{$\mathfrak{p}$\dash local} if~$X\cong X_{\mathfrak{p}}$.
\end{definition}

So now we have the notion of~$\mathfrak{p}$\dash local objects and~$\mathfrak{p}$\dash torsion objects.

\begin{definition}
  For~$\mathfrak{p}\in\Spec R$ we set the \emph{local cohomology} of an object~$X$ to be
  \begin{equation}
    \Gamma_{\mathfrak{p}}(X)\coloneqq\Gamma_{\VV(\mathfrak{p}}\circ\LL_{\ZZ(\mathfrak{p})}(X)=\Gamma_{\VV(\mathfrak{p})}(X_{\mathfrak{p}}).
  \end{equation}
  This is an idempotent functor, and~$X\in\Gamma_{\mathfrak{p}}(\mathcal{T})$ if and only if~$X$ is both~$\mathfrak{p}$\dash local and~$\mathfrak{p}$\dash torsion.
\end{definition}

\begin{remark}
  The notation is not a coincidence: it coincides with Grothendieck's local cohomology functor in the appropriate setting.
\end{remark}

\begin{lemma}
  Let~$V$ and~$W$ be specialisation-closed subsets of~$\Spec R$ such that~$V\setminus W=\{\mathfrak{p}\}$. Then
  \begin{equation}
    \Gamma_V\circ\Gamma_W\cong\Gamma_{\mathfrak{p}}\cong\Gamma_W\circ\Gamma_V.
  \end{equation}
\end{lemma}
This can for instance be applied to~$V=\VV(\mathfrak{p})$ and~$W=\ZZ(\mathfrak{p})$.

\subsection{Stratification of big triangulated categories}
We now have the necessary tools to introduce stratification.
\begin{definition}
  Let~$X$ be an object of~$\mathcal{T}$, with~$R$ acting on~$\mathcal{T}$. Then
  \begin{equation}
    \supp_R X\coloneqq\left\{ \mathfrak{p}\in\Spec R\mid\Gamma_{\mathfrak{p}}(X)\neq 0 \right\}
  \end{equation}
  is the \emph{support} of~$X$.
\end{definition}
\begin{remark}
  If~$X\to Y\to Z\to$ is an exact triangle, then
  \begin{equation}
    \supp_R Y\subseteq\supp_R X\cup\supp_R Y
  \end{equation}
  and
  \begin{equation}
    \supp_R(\coprod_{i\in I}X_i)=\bigcup_{i\in I}\supp_R X_i.
  \end{equation}
\end{remark}

\begin{theorem}
  For an object~$X$ of~$\mathcal{T}$ we have
  \begin{equation}
    \supp_R X=\bigcup_{C\in\mathcal{T}^\cc}\min\{\Supp_R\Hom_{\mathcal{T}}^\bullet(X,Y)\}
  \end{equation}
  where
  \begin{equation}
    \Supp_R M\coloneqq\left\{ \mathfrak{p}\in\Spec R\mid M_{\mathfrak{p}}\neq 0 \right\}
  \end{equation}
  and
  \begin{equation}
    \min\mathcal{U}\coloneqq\left\{ \mathfrak{p}\in\mathcal{U}\mid\mathfrak{q}\in\mathcal{U},\mathfrak{q}\subseteq\mathfrak{p}\Rightarrow\mathfrak{q}=\mathfrak{p} \right\}.
  \end{equation}
\end{theorem}
Hence the minimal elements determine the support: as we are working with specialisation-closed subsets, the support~$\supp_R$ only considers the minimal primes.

As we have assumed~$\mathcal{T}$ to be compactly generated we get the following corollary.
\begin{corollary}
  For all objects~$X$ in~$\mathcal{T}$ we have~$\supp_R X=\emptyset$ if and only if~$X=0$.
\end{corollary}

We now come to the main definition of the lecture series.
\begin{definition}
  The category~$\mathcal{T}$ is \emph{stratified (by the action of~$R$)} if
  \begin{enumerate}
    \item we have that
      \begin{equation}
        \Loc(X)=\Loc(\{\Gamma_{\mathfrak{p}}(X)\mid\mathfrak{p}\in\Spec R\})
      \end{equation}
      for all objects~$X$ in~$\mathcal{T}$, i.e.\ we have the \emph{local-to-global principle} which says that objects are built up from~$\mathfrak{p}$\dash local and~$\mathfrak{p}$\dash torsion information;
    \item $\Gamma_{\mathfrak{p}}(\mathcal{T})$ has no proper localising subcategories, for all~$\mathfrak{p}\in\Spec R$.
  \end{enumerate}
\end{definition}

\begin{proposition}
  Let~$\mathcal{T}$ be as above.
  \begin{enumerate}
    \item The local-to-global principle holds whenever~$\dim R<+\infty$, or when~$\mathcal{T}$ ``has a model.''
    \item Suppose that the local-to-global-principle holds, then we have bijections
      \begin{equation}
        \begin{aligned}
          \left\{ \text{localising subcategories of $\mathcal{T}$} \right\} & \overset{\longleftrightarrow}{1:1} \left\{ \text{collections of localising subcategories $\mathcal{S}_{\mathfrak{p}}\subseteq\mathcal{T}_{\mathfrak{p}}$ for all~$p\in\Spec R$} \right\} \\
          \mathcal{S}\subseteq\mathcal{T} & \longmapsto (\mathcal{S}\cap\Gamma_{\mathfrak{p}}(\mathcal{T}))_{\mathfrak{p}\in\Spec R}.
        \end{aligned}
      \end{equation}
  \end{enumerate}
\end{proposition}

\begin{example}
  \begin{enumerate}
    \item Neeman: $\derived(A)$ is stratified by~$R=A$, where~$A$ is a commutative noetherian ring.
    \item Benson--Iyengar--Krause: $\StMod(kG)$ is stratified by~$\HH^\bullet(G,k)$ (where~$G$ is a finite~$p$\dash group).
  \end{enumerate}
\end{example}

\subsection{Consequences of stratification}
\begin{theorem}
  Suppose that~$\mathcal{T}$ is stratified by~$R$. Then we have a bijection
  \begin{equation}
    \begin{aligned}
      \left\{ \text{localising subcategories of~$\mathcal{T}$} \right\} & \overset{longleftrightarrow}{1:1} \left\{ \text{subsets of $\supp_R(\mathcal{T})$} \right\} \\
      \mathcal{S}\subseteq\mathcal{T} & \longmapsto\supp_R(\mathcal{S})\coloneqq\bigcup_{X\in S}\supp_R X.
    \end{aligned}
  \end{equation}
\end{theorem}

We say~$\mathcal{T}$ is \emph{noetherian} if~$\Hom_{\mathcal{T}}^\bullet(X,Y)$ is finitely generated over~$R$ for all compact objects~$X$ and~$Y$ of~$\mathcal{T}$.
\begin{lemma}
  If~$\End_{\mathcal{T}}^\bullet(X)$ is noetherian then~$\supp_R X=\VV(\mathfrak{a})$, for~$\mathfrak{a}\coloneqq\ker(R\to\End_{\mathcal{T}}^\bullet(X))$.
\end{lemma}
This allows us to classify thick subcategories of~$\mathcal{T}^\cc$!
\begin{theorem}
  Let~$\mathcal{T}$ be as above, and assume moreover that~$\mathcal{T}$ is noetherian. Then we have a bijection
  \begin{equation}
    \begin{aligned}
      \left\{ \text{thick subcategories of~$\mathcal{T}^\cc$} \right\} & \overset{\longleftrightarrow}{1:1}\left\{ \text{specialisation-closed subsets of $\Spec R$} \right\} \\
      \mathcal{S}\subseteq\mathcal{T}^\cc & \longmapsto\supp_R(\mathcal{S}).
    \end{aligned}
  \end{equation}
\end{theorem}
\begin{corollary}
  Let~$\mathcal{T}$ be as above, and assume moreover that~$\mathcal{T}$ is noetherian. Then for all compact objects~$X$ and~$Y$ of~$\mathcal{T}$ we have
  \begin{equation}
    \Supp_R\Hom_{\mathcal{T}}^\bullet(X,Y)=\supp_R X\cap\supp_R Y.
  \end{equation}
\end{corollary}

\begin{example}
  \begin{enumerate}
    \item If~$(\mathcal{T},\otimes,\mathbf{1})$ is a tensor triangulated category then~$\mathcal{T}$ is~$\End_{\mathcal{T}}^\bullet(\mathbf{1})$-linear, and we obtain a calssification of tensor ideal localising subcategories. This generalises the classification of localising subcategories to any finite group~$G$, without the assumption on the order of~$G$.
    \item Let~$A$ be a finite-dimensional~$k$\dash algebra. If we wish to stratify~$\derived(A)$ we run into problems: the center can be \emph{too small}:
      \begin{enumerate}
        \item take~$A=kG$ for~$G$ a finite group, then~$\derived(A)^\cc\cong\proj/A$, but we'd rather study~$\stmod(A)$;
        \item take~$A=kQ$ for~$Q$ an acyclic quiver, then~$\centre^\bullet(\derived(A))=k$ if~$Q$ is Dynkin, which is of no use to us.
      \end{enumerate}
    \item On the other hand, $\centre^\bullet(\mathcal{T})$ can also be \emph{too big} for meaningful calculations, in which case we will often take~$\HH^\bullet(A/k)$ as the ring action on~$\mathcal{T}$.
  \end{enumerate}
\end{example}


\section{Day 4: $\mathbf{K}(\Inj/X)$ and Grothendieck duality}
\subsection{$\derived^\bounded(X)$ and compact objects}

\subsection{Grothendieck duality}


\section{Day 5: Stratification of small triangulated categories}
\subsection{Example: stratifying the bounded derived category of the Kronecker algebra}

\subsection{Stratification of bounded derived categories of hereditary algebras}

\subsection{Stratification of small triangulated categories}

\end{document}

